\section{Compiling}
\subsection{Windows}

To compile this application, you need to have \textbf{CMake}  and \textbf{GNU
Make} installed your system.  The easiest way to do this is by using the \textbf{scoop
package manager}. \textbf{Scoop} is a package manager for windows that automates the
installation of a plethora of applications through the command line. You can learn more about it
\href{https://github.com/ScoopInstaller/Scoop}{here}.

\subsubsection{Installing Scoop}


To install scoop, open powershell and run the following command:

\begin{lstlisting}[language=bash]
iwr -useb get.scoop.sh | iex
\end{lstlisting}

If you get an error you might need to change the execution policy (i.e. enable Powershell), to do so run the following command and redo the command above.

\begin{lstlisting}[language=bash]
Set-ExecutionPolicy RemoteSigned -scope CurrentUser
\end{lstlisting}

Confirm that you have successfully installed scoop, by running the following command

\begin{lstlisting}[language=bash]
scoop --help
\end{lstlisting}

If the installation was successful, you will be able to see the following:
\begin{lstlisting}
Usage: scoop <command> [<args>]

Some useful commands are:

alias       Manage scoop aliases
bucket      Manage Scoop buckets
cache       Show or clear the download cache
\end{lstlisting}

\subsubsection{Installing Scoop}
Once you have successfully installed \textbf{scoop}.

\subsubsection{Installing CMake and GNU Make}
To install \textbf{CMake} and \textbf{GNU Make} run the following
command:

\begin{lstlisting}[language=bash]
 scoop install cmake make 
\end{lstlisting}
 
To check whether the installation is successful for \textbf{GNU Make} run the following command:

\begin{lstlisting}[language=bash]
make --help
\end{lstlisting}

You will be able to see the following:
\begin{lstlisting}
 Usage: make [options] [target] ...
 Options:
   -b, -m                      Ignored for compatibility.
   -B, --always-make           Unconditionally make all targets.
   -C DIRECTORY, --directory=DIRECTORY
                                   Change to DIRECTORY before doing anything
\end{lstlisting}
    
To check whether the installation is successful for \textbf{CMake} run the following command:

\begin{lstlisting}[language=bash]
cmake --help
\end{lstlisting}

You will be able to see the following:

\begin{lstlisting}[language=bash]
Usage

    cmake [options] <path-to-source>
    cmake [options] <path-to-existing-build>
    cmake [options] -S <path-to-source> -B <path-to-build>

Specify a source directory to (re-)generate a build system for it in the
current working directory.  Specify an existing build directory to
re-generate its build system.
\end{lstlisting}

\subsubsection{Compiling the game}

This project is configured to only work with
the MingGW Compiler, so make that it is installed on your computer.

Once you have installed \textbf{CMake} and \textbf{GNU Make}, you may now
compile the application. To do so, navigate to the \codeword{ghostless-pacman}
folder and run.
 
\begin{lstlisting}[language=bash]
make build
\end{lstlisting}

This command will automatically download external GUI libraries which were used
in making the game. After that it will compile the program and place it to the
\codeword{bin} folder.

\subsubsection{Running the game}

Now the only thing left is to run the application, you can navigate to the \codeword{bin}
folder and open the \codeword{ghostless-pacman.exe} file which will run the game. Or you
can run the following command below, to compile and run the application automatically.

\begin{lstlisting}[language=bash]
make run
\end{lstlisting}

Note that, it is important to avoid moving the executable since Windows will not
be able to find the DLLs which are required for running the game.

Hooray! You have now compiled and run the application.

\subsection{Linux}

\subsubsection{Installing the dependencies}

Use your distribution’s package manager to install the following packages:

\begin{itemize}
    \item cmake
    \item make
    \item SDL2
    \item SDL2 Mixer
    \item SDL2 Image
\end{itemize}

\subsubsection{Compiling the source code}
Navigate to the \codeword{ghostless-pacman} folder and run the 
following command.

\begin{lstlisting}[language=bash]
make run
\end{lstlisting}

Hooray! You have now compiled and run the application.
